%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Journal Article
% LaTeX Template
% Version 1.4 (15/5/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[twoside,twocolumn]{article}

%\usepackage[showframe, left=2cm, right=2cm, top=32mm, bottom=32mm, columnsep=25pt]{geometry}% http://ctan.org/pkg/geometry
\usepackage{graphicx}% http://ctan.org/pkg/graphicx
\usepackage[left=2cm, right=2cm, top=32mm, bottom=30mm, columnsep=25pt]{geometry}
\usepackage{stfloats}


\makeatletter
\renewcommand{\fnum@figure}{Fig. \thefigure}
\makeatother


\usepackage{blindtext} % Package to generate dummy text throughout this template 

\usepackage[sc]{mathpazo} % Use the Palatino 
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

\usepackage[english]{babel} % Language hyphenation and typographical rules

%\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float}
\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text

\usepackage{enumitem} % Customized lists
\setlist[itemize]{noitemsep} % Make itemize lists more compact
\usepackage{graphicx}

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
%\renewcommand\thesubsection{\thesection.\alph{subsection}} % roman numerals for subsections
%\renewcommand\thesubsubsection{\thesubsection.\alph{subsubsection}}
\titleformat{\section}[block]{\Large\scshape\centering}{\thesection.}{2em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{0.5em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Department of health science and technology, Aalborg University} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

\usepackage{titling} % Customizing the title section

\usepackage{hyperref} % For hyperlinks in the PDF

\usepackage[utf8]{inputenc}
\usepackage[numbers]{natbib}	
\usepackage[most]{tcolorbox}


\usepackage{subcaption}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\setlength{\droptitle}{-4\baselineskip} % Move the title up

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{\huge Prediction of pain duration and pain intensity \newline from patellofemoral pain maps using a \newline deep learning approach} % Article title
\author{%
\textsc{Birgithe Kleemann Rasmussen, Ignas Kupcikevičius,} \\
\textsc{Linette Helena Poulsen, Mads Kristensen}
 \\[1ex] % Your name
\normalsize Aalborg University \\ % Your institution
% Your email address
%\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
%\textsc{Jane Smith}\thanks{Corresponding author} \\[1ex] % Second author's name
%\normalsize University of Utah \\ % Second author's institution
%\normalsize \href{mailto:jane@smith.com}{jane@smith.com} % Second author's email address
}
\date{December 20, 2017} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{%

\begin{abstract}
\noindent
\textbf{Introduction:} Patellofemoral pain (PFP) syndrome is a musculoskeletal condition that presents as pain behind or around the patella without known structural changes [1]. Partial correlations between perceived size of PFP from pain maps and pain duration along with pain intensity has been indicated in previous studies [2], however morphology and location of PFP remains unexplored in terms of correlation. Based on the object detection capabilities of deep learning methods can be used to detect image-features related to morphology and location. The aim of this study was to determine the performance of deep learning models for predicting pain duration and pain intensity, based on morphology and location of perceived PFP from pain maps.

\noindent
\textbf{Methods and materials:} PFP drawings were collected on a body-schema and encoded into three different pain map representations in respect of morphology of pain, location of pain, and a combination of morphology and location. The distribution of the outputs were analysed and used for defining the classification intervals for pain duration, to which the intervals were below 12 months and above 36 months, and pain intensity, below 4 and above 8 on VAS.
Estimation of generalization performance of the models was calculated during the training.

\noindent
\textbf{Results:} The results during training showed a higher accuracy for pain intensity classification than pain duration classification using morphology-representation. Pain intensity had an accuracy on 65.04\%, and pain duration had an accuracy on 59.51\%.
\noindent
Furthermore, the combined-representation performed with the highest accuracy on 65.14\%. The location and morphology-representation scored 63.33\%, and 65.04\%, respectively, based on pain intensity. 

\noindent
\textbf{Discussion:} Despite pain intensity being defined as multidimensional and subjective, the performance accuracy were higher than that of pain duration. The results may indicate that a combination of the morphology and the location of the pain had a higher classification performance in relation to pain duration or intensity. Currently, it is unclear if deep learning methods may be a suitable approach for classifying PFP syndrome to work as support in clinical settings, to which further investigation is necessary. Improvements could be found when more data become available to better reflect generalization patterns in PFP drawings.
\end{abstract}
}

%----------------------------------------------------------------------------------------
%\usepackage[left=2cm, right=2cm, top=32mm, bottom=32mm, columnsep=25pt]{geometry}
\begin{document}

% Print the title
\maketitle

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\section{Introduction}
\input{Introduction/introduction}

%------------------------------------------------

\section{Methods}
\input{Introduction/method}


%------------------------------------------------

\section{Results}
\input{Results/result}

%------------------------------------------------

\newpage
\section{Discussion}
\input{Results/discuss}

%------------------------------------------------

\section{Conclusion}
\input{Results/conclusion}

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

%\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template
%
%\bibitem[Figueredo and Wolf, 2009]{Figueredo:2009dg}
%Figueredo, A.~J. and Wolf, P. S.~A. (2009).
%\newblock Assortative pairing and life history strategy - a cross-cultural
%  study.
%\newblock {\em Human Nature}, 20:317--330.
% 
%\end{thebibliography}

%----------------------------------------------------------------------------------------
\begingroup
\raggedright
\begin{scriptsize}
\bibliographystyle{unsrtnat}
\bibliography{bib}
%\urlstyle{same}
%
%
%\printbibliography
%\cleardoublepage
\end{scriptsize}
\endgroup
\end{document}