\section{Machine learning}
Machine learning describes the use of algorithms to make a computer able to recognise patterns from different examples and data. Machine learning is a method there uses inductive inference, which identifies rules in a dataset from given input and output. If the computer learns this feature, it can be used to make intelligent decisions and predict specific outcomes.\citep{Nielsen2010}
It is a field that has seen a lot of progress over the past decades, partially because developers recognize the ease in training a system only using examples of the desired in- and output behavior. This is simply easier than trying to manually write a piece of code that anticipate different scenarios from different types input.\citep{Jordan2015}



Machine learning (ML) describes the use of algorithms to make a system able to identify different data types, like images or text, for transcription of speech into text, matching news items, posts or selection of relevant results of search \citep{LeCun2015}.
ML is a method there uses inductive inference, which identifies rules in a dataset from given input and output \citep{Nielsen2010}. If the computer learns this feature, it can be used to make intelligent decisions and predict specific outcomes. \citep{Nielsen2010}
It is a field that has seen a lot of progress over the past decades, partially because developers recognize the ease in training a system only using examples of the desired in- and output behavior. This is simply easier than trying to manually write a piece of code that anticipate different scenarios from different types input. \citep{Jordan2015}


